%% DnD 5e-styled CV for Omar Derkaoui
%% Compile: TEXINPUTS=./lib//: pdflatex cv.dnd.tex

\documentclass[10pt,a4paper,twoside,openany,nodeprecatedcode]{dndbook}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}

\hypersetup{urlcolor=PhbDarkRed}

\begin{document}

%% ── HEADER ──────────────────────────────────────────────────────────────────
\begin{center}
  {\fontsize{32}{38}\DndFontChapter\selectfont Omar Derkaoui}\\[6pt]
  {\large\itshape Backend Software Engineer}\\[10pt]
  {\small
    \faEnvelope\;\href{mailto:omarderkaoui1337@gmail.com}{omarderkaoui1337@gmail.com}
    \quad\textbar\quad
    \faPhone\;+212\,6\,76\,26\,74\,94
    \quad\textbar\quad
    \faGithub\;\href{https://github.com/gundam1337}{github.com/gundam1337}
    \quad\textbar\quad
    \faGlobe\;\href{https://omarderkaoui.cc}{omarderkaoui.cc}
  }
\end{center}

\vspace{4pt}

%% ── ADVENTURER'S DOSSIER (Profile) ──────────────────────────────────────────
\begin{DndReadAloud}
  Backend-focused software engineer with a track record of shipping production features in
  fintech and trading platforms. Specialized in NestJS, PostgreSQL/Oracle, and integrating
  complex legacy banking systems. 1337 Coding School graduate with strong systems fundamentals
  from C/C++ and a mathematical background that brings rigor to backend architecture and
  problem-solving.
\end{DndReadAloud}

\vspace{6pt}

%% ── TWO-COLUMN LAYOUT ───────────────────────────────────────────────────────
\setlength{\columnsep}{18pt}
\begin{multicols}{2}

%% ── CHARACTER SHEET ─────────────────────────────────────────────────────────
\begin{DndMonster}[width=\linewidth]{Omar Derkaoui}
  \DndMonsterType{Backend Engineer, Chaotic Good}

  \DndMonsterBasics[
    armor-class = {Production-hardened (NestJS + Prometheus)},
    hit-points  = {\DndDice{6d8+15} --- 6 UAT-tested features shipped},
    speed       = {Ship fast. Debug faster. Iterate always.},
  ]

  \DndMonsterAbilityScores[
    str = 10,
    dex = 14,
    con = 16,
    int = 18,
    wis = 14,
    cha = 12,
  ]

  \DndMonsterDetails[
    skills    = {API Design +8, DB Architecture +7, Legacy Integration +7, Systems Design +6},
    senses    = {Darkvision (async flows 60\,ft), Truesight (legacy APIs)},
    languages = {Arabic (Native), French (Prof.), English (Prof.)},
    challenge = {Mid-level (3{,}900 XP)},
  ]

  \DndMonsterSection{Actions}

  \DndMonsterAction{NestJS Mastery}
  Shapes scalable backend services at will. Proficient in TypeORM, JWT/Passport, Redis queues,
  Socket.io, and Prometheus instrumentation.

  \DndMonsterAction{Database Architect}
  Designs and optimizes PostgreSQL and Oracle schemas from scratch; uses targeted indexing to
  eliminate query-latency bottlenecks.

  \DndMonsterAction{Legacy Reverse-Engineering}
  Integrates undocumented SOAP and REST APIs without sandbox access. Succeeds even on a failed
  Intelligence check.

  \DndMonsterSection{Bonus Actions}

  \DndMonsterAction{Full Stack Surge (Recharge 5--6)}
  Switches to Next.js 15, React 19, TypeScript, and Tailwind CSS when the front line falls.
\end{DndMonster}

%% ── SPELLBOOK (Skills) ───────────────────────────────────────────────────────
\section{Spellbook}

\begin{DndComment}{Backend Spells --- Known}
  NestJS \textbullet{} Node.js \textbullet{} Express \textbullet{} PostgreSQL \textbullet{}
  OracleDB \textbullet{} TypeORM \textbullet{} Redis \textbullet{} Socket.io \textbullet{}
  JWT/Passport \textbullet{} Jest \textbullet{} Prometheus \textbullet{} Firebase Admin
  \textbullet{} Nodemailer \textbullet{} Puppeteer
\end{DndComment}

\begin{DndComment}{Frontend Cantrips}
  Next.js\,15 \textbullet{} React\,19 \textbullet{} TypeScript \textbullet{} Tailwind CSS
  \textbullet{} Zustand \textbullet{} TanStack Query \textbullet{} Radix UI \textbullet{}
  Framer Motion \textbullet{} Zod \textbullet{} Axios
\end{DndComment}

\begin{DndComment}{Equipment}
  GitHub Actions \textbullet{} Docker
\end{DndComment}

%% ── TONGUES KNOWN (Languages) ───────────────────────────────────────────────
\section{Tongues Known}

\begin{DndTable}[header=Languages]{lX}
  Language & Proficiency    \\
  Arabic   & Native         \\
  French   & Professional   \\
  English  & Professional   \\
\end{DndTable}

%% ── LEGENDARY TRAITS (Hobbies) ──────────────────────────────────────────────
\section{Legendary Traits}

\begin{itemize}
  \item \textbf{Grandmaster of the Chessboard} --- Peak blitz ELO 2300
  \item \textbf{Seeker of Mathematical Truth} --- Geometry \& Olympiad problems
\end{itemize}

\columnbreak

%% ── QUESTS \& CAMPAIGNS (Experience) ────────────────────────────────────────
\section{Quests \& Campaigns}

\DndFeatHeader{Backend Software Engineer}[FinaMaze \textbar{} Feb\,2025 -- Present \textbar{} Casablanca]
\begin{itemize}
  \item First backend contributor on a B2B fintech platform serving a major Middle Eastern bank,
        where AI-driven asset managers build and rebalance investment portfolios.
  \item Owned end-to-end design and delivery of the onboarding and KYC module, reverse-engineering
        undocumented SOAP APIs without a sandbox environment.
  \item Designed Oracle schemas for authentication, user onboarding, notifications, and messaging;
        optimized critical queries with targeted indexing.
  \item Built the notifications and messaging subsystems with background jobs and queue-based async
        dispatch.
  \item Implemented JWT/Passport authentication and Prometheus instrumentation.
  \item Took 6 features through UAT and pre-production across a 24-person engineering organization.
\end{itemize}

\DndFeatHeader{Backend Developer}[AIKON Mobile App \textbar{} Oct\,2024 -- Feb\,2025 \textbar{} Remote]
\begin{itemize}
  \item Contributed backend features to an iOS social-trading platform combining messaging and
        trading workflows in a single mobile experience.
  \item Designed and built the WhatsApp Business API integration, enabling traders to engage
        through a familiar messaging channel.
  \item Implemented real-time chat with Socket.io; modeled the PostgreSQL schema for messaging
        features and shipped them into production.
  \item Implemented JWT and social login; collaborated with a 6-person cross-functional team.
\end{itemize}

\DndFeatHeader{Full Stack Engineer}[Upwork --- Freelance \textbar{} Feb\,2024 -- Oct\,2024 \textbar{} Remote]
\begin{itemize}
  \item Delivered full-stack web projects for international clients end-to-end: requirements
        through deployment and handover.
  \item Built Node.js/Express backends alongside React frontends with authentication and
        third-party integrations.
  \item First commercial software engineering role; transitioned full-time into tech after
        1337 Coding School.
\end{itemize}

\DndFeatHeader{Mathematics Teacher}[Ministry of National Education \textbar{} Sep\,2021 -- May\,2024 \textbar{} Beni Mellal]
\begin{itemize}
  \item Taught mathematics to high-school students while transitioning into software engineering
        through 1337 Coding School.
  \item Developed strong skills in breaking down complex concepts --- directly applied to
        technical communication and documentation.
\end{itemize}

\DndFeatHeader{Chess Instructor}[Al Akhawayn School \textbar{} 2018 -- 2019 \textbar{} Beni Mellal]
\begin{itemize}
  \item Coached chess to children aged 6--10; competitive player with a peak blitz ELO of 2300.
\end{itemize}

%% ── LORE \& TRAINING (Education) ────────────────────────────────────────────
\section{Lore \& Training}

\DndFeatHeader{Computer Science --- Common Core}[1337 Coding School \textbar{} Dec\,2018 -- Jun\,2022 \textbar{} Khouribga]
\begin{itemize}
  \item Intensive peer-led, project-based program (Moroccan branch of 42 Network); no lectures.
  \item Specialized in low-level systems and computer graphics with C/C++; built a multi-threaded
        ray tracer rendering complex scenes with realistic lighting.
\end{itemize}

\DndFeatHeader{BSc Electronic Engineering \& Telecommunications}[FST Beni Mellal \textbar{} 2015 -- 2019]
\begin{itemize}
  \item Coursework in electronics, signal processing, telecommunications, and industrial computing.
\end{itemize}

\end{multicols}

\end{document}
