%%%%%%%%%%%%%%%%%
% This CV template uses altacv.cls
%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

% Change the page layout if you need to
\geometry{left=1cm,right=8.5cm,marginparwidth=6.3cm,marginparsep=1.2cm,top=1.25cm,bottom=1cm,footskip=2\baselineskip}

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% Change the colours if you want to
\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey} 
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}

\name{Omar Derkaoui}
\tagline{Full Stack Developer}
\personalinfo{%
  \email{omarderkaoui1337@gmail.com}
  \phone{0762674942}
  \github{github.com/gundam1337}
  \homepage{omarderkaoui.cc}
}

%% Make the header extend all the way to the right
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Sidebar content is in page1sidebar.tex
\cvsection[page1sidebar]{Professional Experience}

\cvevent{Full-stack Developer}{FinaMaze}{Feb 2025 -- Present}{Casablanca, Morocco}
\begin{itemize}
\item Developed and maintained full-stack features for the FinaMaze platform.
\item Collaborated with cross-functional teams to design and implement scalable web solutions.
\item Worked on both front-end interfaces and back-end APIs in a full-time capacity.
\end{itemize}
\divider

\cvevent{Backend Developer}{AIKON Mobile App}{Oct 2024 -- Feb 2025}{Remote}
\begin{itemize}
\item Worked as a backend developer for the AIKON mobile app (``Connecting Traders''), responsible for designing and implementing RESTful APIs, database schemas, and integration with trading services.
\item Part-time role contributing to a fast-paced startup environment.
\end{itemize}
\divider

\cvevent{Full Stack Engineer}{Upwork (Freelance)}{Feb 2024 -- Oct 2024}{Remote}
\begin{itemize}
\item Delivered full-stack web development projects for diverse clients on the Upwork platform.
\item Built user interfaces and robust back-end services using modern web technologies.
\item Managed client relationships from requirements gathering to final delivery.
\end{itemize}
\divider

\cvevent{Mathematics Teacher}{Minist\`ere de l'\'Education Nationale (Maroc)}{Sep 2021 -- May 2024}{Beni Mellal, Morocco}
\begin{itemize}
\item Taught mathematics to high school students, developing lesson plans and assessing student performance.
\item On-site full-time position within the Moroccan national education system.
\end{itemize}

\cvsection{Education}

\cvevent{Bachelor of Science and Technology}{FST Beni Mellal}{2015 -- 2019}{Beni Mellal, Morocco}
\begin{itemize}
\item Electronic Engineering and Telecommunications. Comprehensive program covering electronics, telecommunications, information processing, and industrial computing.
\end{itemize}

\divider

\cvevent{Junior Developer Program}{1337 Coding School}{Dec 2018 -- Jun 2022}{}
\begin{itemize}
\item Innovative IT training based on peer-learning and project-based learning. Gained hands-on experience in coding and creative problem-solving.
\end{itemize}

\medskip

\end{document}
